---
title: "stegastes_visualization"
author: "JT_Miller"
date: "5/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(plyr)
library(dplyr)
library(ggplot2)
library(tidyr)
library(psych)
library(corrplot)
library(RColorBrewer)
```



```{r}
moorea_fish <- read.csv("MCR_LTER_Annual_Fish_Survey_20210108.csv") #Loading in the data from the moorea LTER
```


```{r}
stegastes <- dplyr::filter(moorea_fish, Taxonomy %in% c("Stegastes punctatus" , "Stegastes nigricans" , "Stegastes fasciolatus" , "Stegastes albifasciatus")) #Selecting specific species that start with the genus Stegastes
```

#We want to look at the population over a time series, so lets clean up the data and plot it in regards to size per time point

```{r}
#make a new dataset that only has stegastes of particular interest. These two species seem to show up the most in comparison to the others.  
stegastes1 <- subset(moorea_fish, Taxonomy == "Stegastes nigricans" | Taxonomy == "Stegastes fasciolatus" )

#change all of the N/A to 0
stegastes1$Biomass[is.na(stegastes1$Biomass)] <- 0

#summarize count by year, site, Taxonomy, and habitat type
stegastes_sum <- stegastes1 %>%
  dplyr:: group_by(Year, Site, Taxonomy, Habitat) %>% 
  dplyr:: summarise(abundance = sum(Count,  na.rm=TRUE)) 
                    
#make new data set that doesn't have 0's so we can take an average size

stegastes_s <- subset(moorea_fish, Taxonomy =="Stegastes nigricans" | Taxonomy == "Stegastes fasciolatus" )
stegastes_clean <- stegastes_s %>% drop_na(Biomass)

#summarize average size by year, Taxonomy, site and habitat
stegastes_size <- stegastes_clean %>%
  dplyr:: group_by(Year, Taxonomy, Site, Habitat) %>% 
  dplyr:: summarise(mean_biomass = mean(Biomass,  na.rm=TRUE),
                     N = length(Biomass),
                    SE = sd(Biomass, na.rm=TRUE)/sqrt(N),
                    count = sum(Count, na.rm=TRUE)) 
stegastes_size_clean <- stegastes_size %>% drop_na(SE)

```
```{r}
stegastes_size_clean$Year <- as.numeric(as.character(stegastes_size_clean$Year)) #Had to do this to fix the graph. 

```

#Looking at a plot of the populations of stegastes through time divided by site. 
```{r}

ggplot(stegastes_size_clean, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() +
  facet_wrap( ~ Site) 
#str(stegastes_size_clean)
```
#Lets divide it up by site and look at these a bit closer, also divide it up by habitat of fringing reef, forereef, and backreef. 

##Site 1
```{r}
stegastes_size_clean_1 <- stegastes_size_clean %>% 
  filter(Site == "1")

ggplot(stegastes_size_clean_1, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() + scale_color_manual(values=c("Green", "Blue")) + ggtitle("Stegastes Count Site 1") +
  facet_wrap(~Habitat)


stegastes_size_clean_1_BA <- stegastes_size_clean_1 %>% 
  filter(Habitat == "BA")
stegastes_size_clean_1_FO <- stegastes_size_clean_1 %>% 
  filter(Habitat == "FO")
stegastes_size_clean_1_FR <- stegastes_size_clean_1 %>% 
  filter(Habitat == "FR")

ggplot(stegastes_size_clean_1_BA, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal()

ggplot(stegastes_size_clean_1_FO, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal()

ggplot(stegastes_size_clean_1_FR, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal()
```
##Site 2
```{r}
stegastes_size_clean_2 <- stegastes_size_clean %>% 
  filter(Site == "2")

ggplot(stegastes_size_clean_2, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() +  scale_color_manual(values=c("Green", "Blue")) +ggtitle("Stegastes Count for Site 2") +
  facet_wrap(~Habitat)

stegastes_size_clean_2_BA <- stegastes_size_clean_2 %>% 
  filter(Habitat == "BA")
stegastes_size_clean_2_FO <- stegastes_size_clean_2 %>% 
  filter(Habitat == "FO")
stegastes_size_clean_2_FR <- stegastes_size_clean_2 %>% 
  filter(Habitat == "FR")

ggplot(stegastes_size_clean_2_BA, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() +  scale_color_manual(values=c("Green", "Blue")) + ggtitle ("Stegastes Count in BackReef Site 2")

ggplot(stegastes_size_clean_2_FO, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal()+  scale_color_manual(values=c("Green")) + ggtitle ("Stegastes Count in ForeReef Site 2")

ggplot(stegastes_size_clean_2_FR, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal()+  scale_color_manual(values=c( "Green", "Blue")) + ggtitle ("Stegastes Count in FringeReef Site 2")
```
##Site 3
```{r}
stegastes_size_clean_3 <- stegastes_size_clean %>% 
  filter(Site == "3")

ggplot(stegastes_size_clean_3, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() +  scale_color_manual(values=c("Green", "Blue")) +ggtitle("Stegastes Count for Site 3")

stegastes_size_clean_3_BA <- stegastes_size_clean_3 %>% 
  filter(Habitat == "BA")
stegastes_size_clean_3_FO <- stegastes_size_clean_3 %>% 
  filter(Habitat == "FO")
stegastes_size_clean_3_FR <- stegastes_size_clean_3 %>% 
  filter(Habitat == "FR")

ggplot(stegastes_size_clean_3_BA, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() +  scale_color_manual(values=c("Green", "Blue")) + ggtitle ("Stegastes Count in BackReef Site 3")

ggplot(stegastes_size_clean_3_FO, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal()+  scale_color_manual(values=c("Green")) + ggtitle ("Stegastes Count in ForeReef Site 3")

ggplot(stegastes_size_clean_3_FR, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal()+  scale_color_manual(values=c("Blue")) + ggtitle ("Stegastes Count in FringeReef Site 3")
```
##Site 4
```{r}
stegastes_size_clean_4 <- stegastes_size_clean %>% 
  filter(Site == "4")

ggplot(stegastes_size_clean_4, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() + scale_color_manual(values=c("Green", "Blue")) + ggtitle("Stegastes Count site 4") 

stegastes_size_clean_4_BA <- stegastes_size_clean_4 %>% 
  filter(Habitat == "BA")
stegastes_size_clean_4_FO <- stegastes_size_clean_4 %>% 
  filter(Habitat == "FO")
stegastes_size_clean_4_FR <- stegastes_size_clean_4 %>% 
  filter(Habitat == "FR")

ggplot(stegastes_size_clean_4_BA, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() +  scale_color_manual(values=c("Green", "Blue")) + ggtitle ("Stegastes Count in BackReef Site 4")

ggplot(stegastes_size_clean_4_FO, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() + scale_color_manual(values=c("Green", "Blue")) + ggtitle ("Stegastes Count in ForeReef Site 4")

ggplot(stegastes_size_clean_4_FR, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() + scale_color_manual(values=c("Green", "Blue")) + ggtitle ("Stegastes Count in FringingReef Site 4")
```

##Site 5
```{r}
stegastes_size_clean_5 <- stegastes_size_clean %>% 
  filter(Site == "5")

ggplot(stegastes_size_clean_5, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() +  scale_color_manual(values=c("Green", "Blue")) + ggtitle("Stegastes Count Site 5")

stegastes_size_clean_5_BA <- stegastes_size_clean_5 %>% 
  filter(Habitat == "BA")
stegastes_size_clean_5_FO <- stegastes_size_clean_5 %>% 
  filter(Habitat == "FO")
stegastes_size_clean_5_FR <- stegastes_size_clean_5 %>% 
  filter(Habitat == "FR")

ggplot(stegastes_size_clean_5_BA, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() + scale_color_manual(values=c("Green", "Blue")) + ggtitle ("Stegastes Count in BackReef Site 5")

ggplot(stegastes_size_clean_5_FO, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() + scale_color_manual(values=c("Green", "Blue")) + ggtitle ("Stegastes Count in ForeReef Site 5")

ggplot(stegastes_size_clean_5_FR, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() + scale_color_manual(values=c("Green", "Blue")) + ggtitle ("Stegastes Count in FringingReef Site 5")
```

##Site 6
```{r}
stegastes_size_clean_6 <- stegastes_size_clean %>% 
  filter(Site == "6")

ggplot(stegastes_size_clean_6, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() + scale_color_manual(values=c("Green", "Blue")) + ggtitle("Stegastes Count Site 6") +
  facet_wrap(~Habitat)

stegastes_size_clean_6_BA <- stegastes_size_clean_6 %>% 
  filter(Habitat == "BA")
stegastes_size_clean_6_FO <- stegastes_size_clean_6 %>% 
  filter(Habitat == "FO")
stegastes_size_clean_6_FR <- stegastes_size_clean_6 %>% 
  filter(Habitat == "FR")

ggplot(stegastes_size_clean_6_BA, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal()

ggplot(stegastes_size_clean_6_FO, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal()

ggplot(stegastes_size_clean_6_FR, aes(x = Year, y = count,)) + 
  geom_line(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal()
```





##Does biomass differ between habitat type/species?
```{r}
ggplot(stegastes_size_clean_1, aes(x = Year, y = mean_biomass,)) + 
  geom_boxplot(aes(color = Taxonomy), size = 1) +
   scale_color_brewer(palette="Paired") +
  theme_minimal() + scale_color_manual(values=c("Green", "Blue")) + ggtitle("Stegastes Mean Biomass for all Sites over time") +
  facet_wrap(~Habitat,)
```
###Next questions: Does S. fasciolatus and S. nigricans utilize different types of coral gardens? Is one more aggressive towards intruders then the others?

#Data Cited: Brooks, A of Moorea Coral Reef LTER. 2021. MCR LTER: Coral Reef: Long-term Population and Community Dynamics: Fishes, ongoing since 2005. knb-lter-mcr.6.58 doi:10.6073/pasta/a667eed481d9743c69c4209f6479acb4
